Report on Late Winter2013 Production: Image Differencing

### 2013-03-28 W13report.tex

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/normal2.eps} \\
\includegraphics[width=0.9\textwidth]{figures/preconv2.eps} \\
\end{center}
\caption{Pairs of LOCAL,SPATIAL difference images in the case of
  successful image subtraction, similar to
  Figure~\ref{fig_galleryBad}.  The {\it top} set of data are from
  postfiltered analysis, while the {\it lower} set are from
  prefiltered data.  Note that the noise is smoother in the
  prefiltered data due to correlation with the PSF. }
\label{fig_galleryGood}
\end{figure}

\begin{figure}
\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps} \\
\caption{``Heat--map'' detailing the total numbers of 5--sigma false
  positives as a function of two main degrees of freedom: the maximum
  order of basis Laguerre polynomials along the y--axis, and the
  spatial order of the Chebyshev expansion of the spatial model along
  the x--axis.  The {\it left} column shows these results for
  prefiltering, while the {\it right} column shows this for the
  post--filtered analysis.  The best results listed in
  Table~\ref{tab-bestfp10}, with the associated configurations from
  Table~\ref{tab-bestconfig10}, correspond to the minimum in each of the
  subpanels.  }
\label{fp_heatmap}
\end{figure}

\begin{figure}
\includegraphics[width=1.0\textwidth]{figures/cellsize.eps} \\
\caption{False detections with cell size
}
\label{cellsize}
\end{figure}

\begin{figure}
\includegraphics[width=1.0\textwidth]{figures/edge.eps} \\
\caption{Distribution of false detections as a function of the minimum
  distance from the edge of the sensor.  The {\it green} line shows
  the results from a random distribution of points.  The {\it blue}
  lines show the measured distributions, normalized as a probability
  density ($\sum y~\Delta x = 1$).  Error bars come from the square
  root of the number of points in each bin. }
\label{edgedist}
\end{figure}

\begin{figure}
\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps} \\
\caption{Fractional increase in false detections as a function of the
  amplitude of random astrometric offsets added to the coordinates of
  sources before image-to-image registration.  The {\it red}, {\it
    green}, and {\it blue} lines correspond to visits v6866601,
  v6866602, and v6866603 respectively, while the {\it dashed} and {\it
    solid} lines correspond to prefiltering and postfiltering,
  respectively.}
\label{wcsrms}
\end{figure}

\begin{figure}
\includegraphics[width=1.0\textwidth]{figures/wcs_shift.eps} \\
\caption{Fractional increase in false detections as a function of bulk
  astrometric offsets added to the coordinates of sources before
  image-to-image registration.  The {\it red}, {\it green}, and {\it
    blue} lines correspond to visits v6866601, v6866602, and v6866603
  respectively, while the {\it dashed} and {\it solid} lines
  correspond to prefiltering and postfiltering, respectively.}
\label{wcsshift}
\end{figure}

\begin{figure}
\includegraphics[width=0.8\textwidth]{figures/shift.eps} \\
\caption{Figure illustrating the ability of the kernel basis to
  compensate, locally, for the effects of misregistration.  Each
  element of the grid shows a single {\tt KernelCandidate} local
  difference image (visit=6866603, doPreFilter=True).  Columns
  indicate the Gaussian sigma of the basis, which is designed to have
  one Gaussian with the prescribed width, modified to fourth order.
  Rows indicate the amplitude of the astrometric offset that was
  introduced into the Source positions before image-to-image
  registration.  In the {\it top} row, we see that even with a small
  astrometric offset, the sigma=2 basis is unable to produce a quality
  subtraction, because the width is inappropriate for matching the two
  input PSFs (the theoretical Gaussian sigma here is 3.4 pixels).  At
  sigma=4 the basis is able to produce a quality subtraction, and by
  sigma=5 the basis is too large to match the PSFs.  In {\it row 4},
  we show that even for an astrometric offset of 4 pixels (0.8''), the
  sigma=4 basis can produce a reasonable difference image without
  structured residuals.  However, by {\it row 5}, with an offset of 6
  pixels, none of the Gaussians provide a successful local difference
  image.  The ability of the basis to compensate for bulk astrometric
  offsets is a function of the kernel width, and the kernel width is
  itself a function of the two input PSF FWHMs.  Thus there is a
  complicated dependence of the ability of the kernel to shift the
  centroids of stars.  Roughly, in our implementation, the basis may
  compensate for local astrometric residuals at a scale up to $\beta
  \times \sqrt{\sigma_S^2 - \sigma_T^2}$, which is the width of the
  largest Gaussian in our bases.}
\label{kernel_offsets}
\end{figure}

@@

>>>>

\begin{figure}
\begin{center}
\centering{\includegraphics[width=0.9\textwidth]{figures/normal2.eps}} \\
\centering{\includegraphics[width=0.9\textwidth]{figures/preconv2.eps}} \\
\end{center}
\caption{Pairs of LOCAL,SPATIAL difference images in the case of
  successful image subtraction, similar to
  Figure~\ref{fig_galleryBad}.  The {\it top} set of data are from
  postfiltered analysis, while the {\it lower} set are from
  prefiltered data.  Note that the noise is smoother in the
  prefiltered data due to correlation with the PSF. }
\label{fig_galleryGood}
\end{figure}

\begin{figure}
\centering{\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps}} \\
\caption{``Heat--map'' detailing the total numbers of 5--sigma false
  positives as a function of two main degrees of freedom: the maximum
  order of basis Laguerre polynomials along the y--axis, and the
  spatial order of the Chebyshev expansion of the spatial model along
  the x--axis.  The {\it left} column shows these results for
  prefiltering, while the {\it right} column shows this for the
  post--filtered analysis.  The best results listed in
  Table~\ref{tab-bestfp10}, with the associated configurations from
  Table~\ref{tab-bestconfig10}, correspond to the minimum in each of the
  subpanels.  }
\label{fp_heatmap}
\end{figure}

\begin{figure}
\centering{\includegraphics[width=1.0\textwidth]{figures/cellsize.eps}} \\
\caption{False detections with cell size
}
\label{cellsize}
\end{figure}

\begin{figure}
\centering{\includegraphics[width=1.0\textwidth]{figures/edge.eps}} \\
\caption{Distribution of false detections as a function of the minimum
  distance from the edge of the sensor.  The {\it green} line shows
  the results from a random distribution of points.  The {\it blue}
  lines show the measured distributions, normalized as a probability
  density ($\sum y~\Delta x = 1$).  Error bars come from the square
  root of the number of points in each bin. }
\label{edgedist}
\end{figure}

\begin{figure}
\centering{\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps}} \\
\caption{Fractional increase in false detections as a function of the
  amplitude of random astrometric offsets added to the coordinates of
  sources before image-to-image registration.  The {\it red}, {\it
    green}, and {\it blue} lines correspond to visits v6866601,
  v6866602, and v6866603 respectively, while the {\it dashed} and {\it
    solid} lines correspond to prefiltering and postfiltering,
  respectively.}
\label{wcsrms}
\end{figure}

\begin{figure}
\centering{\includegraphics[width=1.0\textwidth]{figures/wcs_shift.eps}} \\
\caption{Fractional increase in false detections as a function of bulk
  astrometric offsets added to the coordinates of sources before
  image-to-image registration.  The {\it red}, {\it green}, and {\it
    blue} lines correspond to visits v6866601, v6866602, and v6866603
  respectively, while the {\it dashed} and {\it solid} lines
  correspond to prefiltering and postfiltering, respectively.}
\label{wcsshift}
\end{figure}

\begin{figure}
\centering{\includegraphics[width=0.8\textwidth]{figures/shift.eps}} \\
\caption{Figure illustrating the ability of the kernel basis to
  compensate, locally, for the effects of misregistration.  Each
  element of the grid shows a single {\tt KernelCandidate} local
  difference image (visit=6866603, doPreFilter=True).  Columns
  indicate the Gaussian sigma of the basis, which is designed to have
  one Gaussian with the prescribed width, modified to fourth order.
  Rows indicate the amplitude of the astrometric offset that was
  introduced into the Source positions before image-to-image
  registration.  In the {\it top} row, we see that even with a small
  astrometric offset, the sigma=2 basis is unable to produce a quality
  subtraction, because the width is inappropriate for matching the two
  input PSFs (the theoretical Gaussian sigma here is 3.4 pixels).  At
  sigma=4 the basis is able to produce a quality subtraction, and by
  sigma=5 the basis is too large to match the PSFs.  In {\it row 4},
  we show that even for an astrometric offset of 4 pixels (0.8''), the
  sigma=4 basis can produce a reasonable difference image without
  structured residuals.  However, by {\it row 5}, with an offset of 6
  pixels, none of the Gaussians provide a successful local difference
  image.  The ability of the basis to compensate for bulk astrometric
  offsets is a function of the kernel width, and the kernel width is
  itself a function of the two input PSF FWHMs.  Thus there is a
  complicated dependence of the ability of the kernel to shift the
  centroids of stars.  Roughly, in our implementation, the basis may
  compensate for local astrometric residuals at a scale up to $\beta
  \times \sqrt{\sigma_S^2 - \sigma_T^2}$, which is the width of the
  largest Gaussian in our bases.}
\label{kernel_offsets}
\end{figure}

@@

\begin{figure}
\centering{\includegraphics[width=0.9\textwidth]{figures/corrA.eps}} \\
\caption{Correlation of the statistics calculated on the control
  sample {\tt KernelCandidates} during the model fitting with the
  number of false positives per sensor coming from
  detection and measurement, for the {\bf postfiltering} pipeline.
  Results for visit v6866601 are shown as {\it red squares}, for
  v6866602 as {\it green circles}, and for v6866603 {\it blue
    triangles}.  Three of the statistics, descibed in
  Section~\ref{sec-stats}, are presented.  They clearly correlate with
  each other.  For the deconvolution visit v6866601, the statistics
  are very poor even for the ``best'' solutions.  
}
\label{corrpost}
\end{figure}

\begin{figure}
\centering{\includegraphics[width=0.9\textwidth]{figures/corrB.eps}} \\
\caption{Correlation of the statistics calculated on the control
  sample {\tt KernelCandidates} during the model fitting with the
  number of false positives per sensor coming from
  detection and measurement, for the {\bf prefiltering} pipeline.
  Results for visit v6866601 are shown as {\it red squares}, for
  v6866602 as {\it green circles}, and for v6866603 {\it blue
    triangles}.  Three of the statistics, descibed in
  Section~\ref{sec-stats}, are presented.  They clearly correlate with
  each other (leftmost panels), and also tend to correlate with the
  number of false detections (rightmost column).}
\label{corrpre}
\end{figure}
